Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/ClementiBarba2020.tex
minor tweaks

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitation of nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with trecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The main result replicates: the wavenumber
    position of the first mode, but for other modes the results differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes.

>>>>

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitations on nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with trecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The results partially replicate: the wavenumber
    position of some mode match, but for other modes they differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes.
